\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape D Fyzan Ahammad} \\ \vspace{10pt}
    \small \raisebox{-0.1\height}\faPhone\ 8309648519 ~ \href{mailto:siddheshdesai777@gmail.com}{\raisebox{-0.1\height}\faEnvelope\  \underline{fyzanahammad@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/fyzanahammad/}{\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/fyzanahammad}{\faGithub\ \underline{Github}} ~
    \href{https://fyzanahammad.github.io/}{\faGlobe\ \underline{Portfolio}}

    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Jamia Millia Islamia, New Delhi}{2020 -- 2024}
      {Bachelor of Technology in Electronics and Communication Engineering }{\textbf{GPA - 8.6}}
    \resumeSubheading
      {Sri Medha, Anantapur}{2017 -- 2019}
      {Class 12}{\textbf{Percentage - 92\%}}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------

\section{Experience}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Deep Learning and Research Intern} $|$ \emph{Enord - AI on Edge Drone Tech Start-Up}}{Feb 2024 - Present}
          \resumeItemListStart
            \resumeItem{Developed and fine-tuned computer vision models using \textbf{YOLOx} object detection framework, achieving over \textit{\textbf{90\%}} accuracy on projects focused on runway foreign object detection and solar panel hotspot detection.}
            \resumeItem{Annotated and prepared datasets comprising \textit{\textbf{30,000}} images for runway foreign object detection and 5,000 images for solar panel hotspot detection, facilitating robust model training.}
            \resumeItem{Trained the YOLOx Tiny Model with \textit{\textbf{5 million parameters}} on \textit{\textbf{AWS EC2}} instance over a period of 2 days, employing \textit{\textbf{SSH}} access for streamlined model optimization and achieving significant performance gains.}
            \resumeItem{Achieved a \textbf{10X} increase in inference speed by optimizing deployment efficiency through the conversion of \textit{\textbf{PyTorch}} model into \textit{\textbf{TensorRT}} format, for facilitating seamless integration with \textit{\textbf{NVIDIA Jetson Nano}} 4gb on drones.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
    \resumeProjectHeading
        {\textbf{Research Intern} $|$ \emph{DR. Zeeshan - JMI, New Delhi}}{Jan 2024 - Apr 2024}
          \resumeItemListStart
            \resumeItem{Conducted in-depth research on Parkinson's disease, integrating deep learning for prediction and severity assessment.}
            \resumeItem{Reviewed numerous research papers to gain insights into current methodologies and opportunities for innovation.}
            \resumeItem{Developed a deep learning model for physiotherapy guidance in Parkinson's disease, utilizing computer vision techniques for enhanced effectiveness.}
          \resumeItemListEnd
          \vspace{-13pt}


\vspace{1pt}


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {{\faGithub}\, \href{https://github.com/fyzanahammad/PDF-Question-Answering-Application-with-Gen-AI.git}{\textbf{RAG Implementation: Extracting Information from PDFs with RAG}} $|$ \emph{Gemini-pro, Langchain, FAISS, Streamlit}}{}
          \vspace{-7pt}
          \resumeItemListStart
            \resumeItem{Engineered a PDF Question Answering Application, integrating Google Generative AI for efficient text processing and answer generation.}
            \resumeItem{Leveraged advanced language technologies like LangChain and LangChain Google GenAI for seamless text handling and conversational AI functionalities.}
          \resumeItemListEnd
          \vspace{-7pt}
          
      \resumeProjectHeading
          {{\faGithub}\, \href{https://github.com/yourusername/repo1}{\textbf{Solar panel Hotspot detection using YOLOv8}} $|$ \emph{YOLOv8, Roboflow, TensorRT, NVIDIA-Jetson}}{}
          \vspace{-7pt}
          \resumeItemListStart
            \resumeItem{Developed Solar Panel Hotspot Detection using YOLOv8, enhancing efficiency in identifying potential issues.}
            \resumeItem{Implemented state-of-the-art Computer Vision techniques, and Roboflow for accurate detection.}
            \resumeItem{Optimized model inference speed with TensorRT and deployed on NVIDIA Jetson for real-time monitoring.}
          \resumeItemListEnd 
          \vspace{-7pt}

      \resumeProjectHeading
          {{\faGithub}\, \href{https://github.com/fyzanahammad/Life-Saving-Signs-Real-Time-Detection-of-Emergency-Indian-Sign-Language.git}{\textbf{Life-Saving Signs: Real-Time Detection of Emergency Indian Sign Language}} $|$ \emph{LSTM, Streamlit}}{}
          \vspace{-7pt}
          \resumeItemListStart
            \resumeItem{Engineered Real-time Indian Sign Language Detection using LSTM, improving accessibility for the hearing-impaired community.}
            \resumeItem{Integrated LSTM models for accurate sign language recognition, enhancing communication possibilities.}
            \resumeItem{Developed a user-friendly interface with Streamlit for intuitive interaction and seamless deployment.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-5pt}



%-----------Technical Skills-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, C, C++, HTML/CSS, SQL} \\
     \textbf{Technologies}{: Tensorflow, PyTorch, Keras, Numpy, Pandas, Matplotlib, OpenCV, YOLO, Linux, GitHub, NVIDIA-Jetson} \\
     \textbf{Coursework}{: Data Structures and Algorithms, Object Oriented Programming, Computer Networks, Operating Systems, Database Management, Data Science, Artificial Intelligence, Machine Learning, Deep Learning } \\
     \textbf{Other Skills}{: UI \& UX Design, Figma, Canva, MS Office, Graphic Designing, Digital Marketing } \\
     \textbf{Languages}{: English(Professional proficiency), Urdu(Native), Telugu(Native), Hindi(Native), Tamil(Elementary Proficiency) } \\
    }}
 \end{itemize}
 \vspace{-16pt}



%-----------Position of Responsibility-----------
\section{Achievements}
    \vspace{-10pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Piranha Tank} $|$ \emph{Finalists in Startup Pitching event}}{\textit{Sept 2022}}
          \vspace{-7pt}
          \resumeItemListStart
            \resumeItem{Stood as \textbf{\textit{finalists}} of Jamia's E-Cell Pirana Tank, highlighting strong presentation and entrepreneurial skills.}
            \resumeItem{Secured \textbf{\textit{incubation}} space at Jamia Millia Islamia.}
          \resumeItemListEnd
          \vspace{-13pt}
      
    \resumeSubHeadingListEnd
\vspace{1pt}

\end{document}
